\documentclass{resume} % Use the custom resume.cls style
\usepackage[left=0.8in, right=0.8in, top=0.7in, bottom=0.7in]{geometry} % Document margins
\usepackage{enumitem}    
\usepackage{color}
%\definecolor{darkblue}{RGB}{46,78,126}
\definecolor{darkblue}{RGB}{0,0,0}
\usepackage[colorlinks,urlcolor=darkblue]{hyperref}
\name{Yuanyuan Shi} % Your name
\address{185 Stevens Way \\ Seattle, WA 98195} % Your address
\address{Tel: (206)9661377 \\ Email: yyshi@uw.edu \\ \href{http://shiyuanyuan.site/}{http://shiyuanyuan.site/}} % Your phone number and email
\newcommand{\comment}[1]{}

\begin{document}
    
    %----------------------------------------------------------------------------------------
    %    EDUCATION SECTION
    %----------------------------------------------------------------------------------------
    \begin{rSection}{Education}
	{\bf University of Washington} \hfill {\bf Seattle, WA} \\ 
	{Ph.D. Candidate in Electrical and Computer Engineering} \hfill {Sep 2015 - Jun 2020 (expected)}
	
	{\bf University of Washington} \hfill {\bf Seattle, WA} \\ 
	{Master of Science in Statistics} \hfill {Sep 2016 - Jun 2020 (expected)}\\
	{Master of Science in Electrical and Computer Engineering} \hfill {Sep 2015 - Jun 2018}
	
	{\bf Nanjing University} \hfill {\bf Nanjing, China} \\ 
	{Bachelor of Engineering in Automation} \hfill {Sep 2011 - Jun 2015}\\
	{Summer Research at University of Toronto, Canada} \hfill {Jun 2014 - Sep 2014}
\end{rSection}

\begin{rSection}{Research interests}
	My research interests are in the area of cyber-physical and energy systems, from the perspective of machine learning, optimization, and control.
\end{rSection}

\begin{rSection}{Publications}    
	\textbf{Preprints}
	\begin{enumerate}[wide, label={[\arabic*]. }, labelindent=0pt]
		\item \textbf{Y. Shi}, M., Qi, C. Ma, R. Yuan, D. Wu, and Z.M. Shen, ``A Practical End-to-End Inventory Management Model with Deep Learning,'' submitted to \emph{Management Science}.
		
		\item \textbf{Y. Shi}, B. Zhang, ``Learning in Cournot Games with Limited Information Feedback'', 
		\emph{\href{https://arxiv.org/abs/1906.06612}{arXiv}}.
		
		\item Y. Chen, \textbf{Y. Shi}, and B. Zhang, ``Data-Driven Optimal Voltage Regulation'', submitted to \emph{Power Systems Computation Conference (PSCC)}, 2020. 
	\end{enumerate}
	\textbf{Journal Papers}
	\begin{enumerate}[wide, label={[\arabic*]. }, labelindent=0pt]
	\setcounter{enumi}{3}
	\item \textbf{Y. Shi}, B. Xu, Y. Tan, D. Kirschen, and B. Zhang, ``Optimal Battery Control Under Cycle Aging Mechanisms in Pay for Performance Settings,'' in \emph{IEEE Transactions on Automatic Control}, 2019.
		
	\item B. Xu, \textbf{Y. Shi}, D. S. Kirschen, and B. Zhang, ``Optimal Battery Participation in Frequency Regulation Markets," in \emph{IEEE Transactions on Power Systems}, 2018
		
	\item \textbf{Y. Shi}, B. Xu, D. Wang, and B. Zhang, ``Using Battery Storage for Peak Shaving and Frequency Regulation: Joint Optimization for Superlinear Gains,'' in \emph{IEEE Transactions on Power Systems}, 2017.
		
	\item L. Zhou, \textbf{Y. Shi}, J. Wang, and P. Yang, ``A Balanced Heuristic Mechanism for Multirobot Task Allocation of Intelligent Warehouses,'' in \emph{Journal of Mathematical Problems in Engineering}, 2014.    
	\end{enumerate}
	
	\textbf{Conference Papers}
	\begin{enumerate}[wide, label={[\arabic*]. }, labelindent=0pt]
	\setcounter{enumi}{7}
	
	\item D. Mankowitz, N. Levine, R. Jeong, A. Abdolmaleki, J. Springenberg, \textbf{Y. Shi}, J. Kay, T. Hester, T. Mann, and M. Riedmiller, ``Robust Reinforcement Learning for Continuous Control with Model Misspecification'', accepted by \emph{International Conference on Learning Representations (ICLR)}, 2020.
	
	\item \textbf{Y. Shi}, K. Xiao, D.J. Mankowitz, R. Jeong, N. Levine, S. Gowal, T. Mann, and T. Hester, ``Data-Driven Robust Reinforcement Learning for Continuous Control'', in \emph{Safety and Robustness in Decision Making Workshop, Neural Information Processing Systems (NeurIPS)}, 2019.
	
	\item K. Xiao, S. Gowal, T. Hester, R. Jeong, D.J. Mankowitz, \textbf{Y. Shi}, and T.W. Weng, ``Learning Neural Dynamics Simulators With Adversarial Specification Training'', in \emph{Safety and Robustness in Decision Making Workshop, Neural Information Processing Systems (NeurIPS)}, 2019.
	
	\item Y. Chen*, \textbf{Y. Shi}*, and B. Zhang, ``Optimal Control Via Neural Networks: A Convex Approach'', in \emph{International Conference on Learning Representations (ICLR)}, 2019.  
		
	\item \textbf{Y. Shi}, B. Xu, Y. Tan, and B. Zhang, ``A convex cycle-based degradation model for battery energy storage planning and operation'', in \emph{Proceedings of American Control Conference (ACC)}, 2018 
		
	\item B. Xu, \textbf{Y. Shi}, D. Kirschen, and B. Zhang, “Optimal regulation response of batteries under cycle aging mechanisms,” in \emph{Proceedings of IEEE Conference on Decision and Control (CDC)}, 2017
		
	\item Y. Chen, \textbf{Y. Shi}, and B. Zhang. ``Modeling and Optimization of Complex Building Energy Systems with Deep Neural Networks.'', in \emph{Asilomar Conference}, 2017.
		
	\item \textbf{Y. Shi}, B. Xu, B. Zhang, and D. Wang, {``Leveraging energy storage to optimize data center electricity cost in emerging power markets."}, in \emph{Proceedings of the Seventh International Conference on Future Energy Systems}, ACM (e-Energy), 2016. 
	\end{enumerate}
\end{rSection}

\begin{rSection}{Invited Talks}  
	\begin{enumerate}[wide, label={[\arabic*]. }, labelindent=0pt]
	\item ``{Data-driven Control for Energy Systems}'', Department of Industrial Engineering and Operations Research, University of California, Berkeley, 2019/11. Hosted by Prof. Javad Lavaei.
	
	\item ``{Data-driven Control for Energy Systems}'', Intelligent System and Control Forum, Nanjing University, China, 2019/10. Hosted by Prof. Chunlin Chen.
	
	\item ``{Data-driven Robust Reinforcement Learning for Continuous Control}'', DeepMind for Google (DMG) Team Meeting, DeepMind, UK, 2019/09. Hosted by Praveen Srinivasan.
	
	\item ``{Optimal Control via Neural Networks}'', Grid Science Winter School and Conference, Los Alamos National Laboratory, New Mexico, 2019/01. Hosted by Dr. Deepjyoti Deka.
	
	\item ``{End-to-End Model for Inventory Management}'', INFORMS Annual Meeting, Arizona, 2018/11.
	
	\item ``{Modeling and Optimization of Complex Building Systems with Recurrent Neural Networks}'', INFORMS Annual Meeting, Texas, 2017/10.
	\end{enumerate}
\end{rSection}

\begin{rSection}{INDUSTRY EXPERIENCES}
	\begin{rSubsection}{Research Intern, DeepMind}{2019/06-2019/09}{Mentors: Dr.Daniel J. Mankowitz, Dr. Timothy Mann, Dr. Todd Hester}
		
		\item We proposed a novel framework for incorporating robustness into continuous control RL algorithms under model uncertainties. It showed improved robust performance in various robotic control tasks.
	\end{rSubsection}
	\begin{rSubsection}{Research Intern, JD.com Silicon Valley Research Center}{2018/06-2018/09}{Mentors: Prof. Zuojun (Max) Shen, Dr. Rong Yuan, Dr. Di Wu}{}
		
		\item We studied the optimal inventory control problem under environmental uncertainties. A new one-step end-to-end (E2E) framework is proposed that outputs order decisions directly from features via a modular neural network. It achieved over 10\% cost saving in JD.com production testing.
	\end{rSubsection}
	\begin{rSubsection}{Power System Research Intern, Doosan GridTech}{2017/06-2017/08}{Mentor: Dr. Tess Williams}{}    
		\item Built optimization models and sensitivity analysis for multiple distributed energy resource projects;
		\item Built statistical and machine learning models for day-ahead electricity price prediction.
	\end{rSubsection}
\end{rSection}
\begin{rSection}{Honors \& Awards}
	\textbf{Irene C. Peden Electrical Engineering Fellowship}, University of Washington, 2019\\
	\textbf{National Science Foundation (NSF) iREDEFINE Award}, NSF, 2019 \\
	\textbf{\href{https://risingstars18-eecs.mit.edu/}{Rising Stars in EECS}}, MIT, 2018 \\
	\textbf{Malvar Endowed Fellowship in Electrical Engineering}, University of Washington, 2018\\
	\textbf{Clean Energy Institute (CEI) Fellowship}, University of Washington, 2017\\
	\textbf{Keith \& Nancy Rattie Endowed Fellowship}, University of Washington, 2016\\
	\textbf{China National Scholarship}, Ministry of Educaction 
	in China, 10/2014 \\
	\textbf{Mitacs Canada Globalink Research Fellowship}, 06/2014\\
	\textbf{Travel Grants and Awards:} 2019 International Conference on Learning Representations (ICLR), 2019 D. E. Shaw Exploration Fellowship, 2019 Grid Science Winter School and Conference,  2018 Clean Energy Institute Travel Award
\end{rSection}
\begin{rSection}{Services}
	\textbf{Journal Reviewer}: IEEE Transactions on Power Systems, IEEE Transactions on Smart Grid, IEEE Transactions on Power Delivery, Journal of Energy Storage, IET Smart Grid
	
	\textbf{Conference Reviewer}: ICLR 2020, ACC 2020, PSCC 2020, IJCAI 2019, SmartGridComm 2019, PES General Meeting 2018
	
	\textbf{Graduate Student Representative}, Curriculum Committee of Electrical and Computer Engineering Department, University of Washington
	
	\textbf{Outreach:} Clean Energy Institute Ambassador for K-12 Students
\end{rSection}    
%------------------
%\begin{rSection}{References}
%	\href{http://zhangbaosen.github.io}{Baosen Zhang}\\
%	Assistant Professor, \\
%	Department of Electrical and Computer Engineering\\
%	University of Washington\\
%	Phone: 206-616-3818, Email: zhangbao@ece.uw.edu
%	
%	\href{http://www2.ee.washington.edu/research/real/real_pe.html}{Daniel Kirschen}\\
%	Professor, \\
%	Department of Electrical and Computer Engineering,\\
%	University of Washington\\
%	Phone: 206-543-2174,
%	Email: kirschen@ece.uw.edu
%	
%	\href{http://shen.ieor.berkeley.edu/}{Zuojun (Max) Shen}\\
%	Professor and Department Chair,\\
%	Department of Industrial Engineering and Operations Research, \\
%	University of California, Berkeley\\
%	Phone: 510-643-2392, Email: maxshen@berkeley.edu
%\end{rSection}
\end{document}
